### 2008-03-17 SAiP/Module1/H3/doc/softwarearchitecture.tex
Grammar fix

\begin{description}
    \item[a. Choose the architectual drivers]
  Here the quality attributes of the system would be defined by the stakeholders of the system and then a vote would be used to determine which of the quality attributes are architectual drivers. The quality attributes would be expressed as quality attribute scenarios.
    \item[b. Choose an architectual pattern]
  Based on the architectual drivers selected in 1, use the mapping in Bass et al. as well as other literature and experience to determine some tactics for achieving the architectual drivers for the system. Then select some architectual patterns to realize the tactics.
    \item[c. Instantiate modules using multiple views]
  Based on the tactics and patterns found above the architecture for the system may be expressed using UML. It is \emph{always} required to use multiple views in order to properly describe the architecture. A good approach is the "3 + 1" structure, which uses three viewpoints; Module viewpoint, Component \& Connector viewpoint and Allocation viewpoint. These three viewpoint is expressed in UML using Package diagrams, Object and sequence diagrams, and deployment diagrams respectively. These diagrams should in the first iteration only look at relations and interactions between the main components (the layers).
    \item[d. Define interfaces]
  Define the interfaces between the main components (the layers).
    \item[e. Verify scenarios and use cases]
  Make sure that the steps a - d covered all the parts of the scenarios. If not include the missing parts and updates the scenarios/architecture is inconsistencies are found.
\end{description}
\subsubsection{Repeat the steps above for every module that needs further decomposition}
The first iteration only look at the overall architecture (the leation and communication between layers). The following iterations will decompose the individual layers and as needed the individual components in the layers.

@@

\fixme{Answer question 1.5}

>>>>

\begin{description}
    \item[a. Choose the architectual drivers]
  Here the quality attributes of the system would be defined by the stakeholders of the system and then a vote would be used to determine which of the quality attributes are architectual drivers. The quality attributes would be expressed as quality attribute scenarios.
    \item[b. Choose an architectual pattern]
  Based on the architectual drivers selected in 1, use the mapping in Bass et al. as well as other literature and experience to determine some tactics for achieving the architectual drivers for the system. Then select some architectual patterns to realize the tactics.
    \item[c. Instantiate modules using multiple views]
  Based on the tactics and patterns found above the architecture for the system may be expressed using UML. It is \emph{always} required to use multiple views in order to properly describe the architecture. A good approach is the "3 + 1" structure, which uses three viewpoints; Module viewpoint, Component \& Connector viewpoint and Allocation viewpoint. These three viewpoints are expressed in UML using Package diagrams, Object and sequence diagrams, and deployment diagrams respectively. These diagrams should in the first iteration only look at relations and interactions between the main components (the layers).
    \item[d. Define interfaces]
  Define the interfaces between the main components (the layers).
    \item[e. Verify scenarios and use cases]
  Make sure that the steps a - d covered all the parts of the scenarios. If not include the missing parts and updates the scenarios/architecture is inconsistencies are found.
\end{description}
\subsubsection{Repeat the steps above for every module that needs further decomposition}
The first iteration only look at the overall architecture (the leation and communication between layers). The following iterations will decompose the individual layers and as needed the individual components in the layers.

@@

There are generally two approaches to creating an architecture, as defined by Bass et. al. and that is to define it in advance, and only define the overall structure and then let it grow from the following implementations.

There are also two reasons for creating an architecture; in order to create a product that exhibits some of the quality attributes defined in the architecture (modifiability, usability, ...) and in order to reuse the architecture (or part of the architecture) as a product line for creating other products. This latter reason is described in section yy.

Creating an architecture up front allows for the definition of all properties of the architecture; the quality attributes and their individual priorities, the individual elements/components and how they interconnect both at runtime and statically, etc. This has the benifit that when the design and implementation phase is begun it may easily be broken down into parallel activities and integrated later, as everyone has a clear picture of what is important and what the interfaces are.

Unfortunately defining the architecture fully up front only makes sense if there is enough information in advance to create the architecture form. Very often there are "dark horses", things that do not become apparent until the design and implementation phase. If it is not believed that sufficient information exist to fully define the architecture, then doing so may not only be a waste, it may lead to the very dangerous loose-loose principle, where e.g. an overhead is introduced to service modifiability, only to be hacked in order to service a performance issue that was not apparent at the architectual design pahse. This means that part of the overhead is preserved (in memory-footprint if nowhere else), without preserving any of the modifiability advantages.

Another requirement to defining the architecture fully up front has to do with the organization. It may be good and dandy to create a fully defined architecture with focus on parallel implementation, if there is only one in-house developer to implement the product.
Based on this the Beer Web Store architect must have decided that there are sufficient information to fully define the architecture and also that there is a reason (parallel implementation, out-sourceing of the design/implementation, etc.).

Asuming that the architect in question has followed the course Software Architecture in Practice, he has obviously looked at the architectual properties, the stake holders, the organization and the requirement and deemed that there is sufficient grounds to fully specify the architecture in advance, with the risks and possible gains that it has.
